Scheeper's Meager-NWD Game and the Menger Game

### 2014-06-30 phd/dissertation/chapter5.tex
begun work on Menger chapter

Results pertaining to the Locally Finite games related to $W$ games.

\section{Characterizations using $\lfkpgame{X}$, $\lfklgame{X}$}

\begin{thm}(G)
  The following are equivalent for a locally compact space $X$:
    \begin{itemize}
      \item $X$ is paracompact
      \item $\pl K \uparrow \lfklgame{X}$.
    \end{itemize}
\end{thm}

\begin{thm}(G)
  The following are equivalent for a locally compact space $X$:
    \begin{itemize}
      \item $X$ is metacompact
      \item $\pl K \tactwin \lfkpgame{X}$.
    \end{itemize}
\end{thm}

\begin{thm}(G)
  The following are equivalent for a locally compact space $X$:
    \begin{itemize}
      \item $X$ is $\sigma$-metacompact
      \item $\pl K \markwin \lfkpgame{X}$.
    \end{itemize}
\end{thm}

\begin{obs}
  The following are equivalent for any space $X$:
    \begin{itemize}
      \item $X$ is compact
      \item $\pl K \ktactwin{0} \lfkpgame{X}$.
    \end{itemize}
\end{obs}

\begin{thm}
  $P \markwin G_{K,P}(X)$ where $X$ is a first-countable non-locally
  countably compact space.
\end{thm}

\begin{thm}
  $P \not\tactwin G_{K,P}(M)$ where $M$ is the metric fan space.
\end{thm}

\begin{thm}
  The following are equivalent for any locally compact space $X$:
    \begin{itemize}
      \item $X$ is Lindel\"of.
      \item $X$ is $\sigma$-compact.
      \item $X$ is hemicompact.
      \item $\pl K \prewin G_{K,L}(X)$.
      \item $\pl K \prewin G_{K,P}(X)$.
    \end{itemize}
\end{thm}

\begin{thm}
  The following are equivalent for any Hausdorff $k$-space $X$:
    \begin{itemize}
      \item $X$ is hemicompact.
      \item $X$ is $k_{\omega}$.
      \item $\pl K \prewin \lfklgame{X}$.
      \item $\pl K \prewin \lfkpgame{X}$.
    \end{itemize}
\end{thm}

\section{Non-locally compact spaces}

\begin{prop}
  If $X=\omega\cup\mathcal{F}\subset\beta\omega$ (a non-$k$ space),
  then $K\not\prewin \lfklgame{X}$.
\end{prop}

\begin{prop}
  If a selective ultrafilter $\mathcal{F}$ exists (independent of ZFC),
  then $K \not\prewin \lfkpgame{X}$
  for $X=\omega \cup \{\mathcal{F}\}\subset \beta\omega$.
\end{prop}

\begin{thm}
  Then there is an ultrafilter $\mathcal{F}$ such that
  then $K \prewin \lfkpgame{X}$ and $K \tactwin \lfkpgame{X}$
  for $X=\omega \cup \{\mathcal{F}\}\subset \beta\omega$.
\end{thm}

\begin{thm}
  Let $M$ be the \term{metric fan}, a non-locally compact $k$ space.
  Then $P \win \lfkpgame{M}$.
\end{thm}

\begin{thm}
  Let $S$ be the \term{sequential fan}, a non-locally compact $k$ space.
  Then $K \prewin \lfkpgame{S}$ and $K\tactwin \lfkpgame{S}$.
\end{thm}

(TODO: Maybe consider claim
$K \prewin \lfkpgame{X}$ $\Rightarrow$ $X$ is a $k$-space)

\section{Cantor tree space example}

\begin{ex}
  Let $X$ be a zero-dimensional, compact L-space
  (hereditarally Lindeloff and non-separable).
  It is a fact that there exists a point-countable collection
  $\mathcal{U}=\{U_\alpha : \alpha<\omega_1\}$ of clopen sets in $X$, and it is
  also true that any point-finite subcollection of $\mathcal{U}$ is countable.

  Let $C = \{c_\alpha : \alpha <\omega_1\}$ be any uncountable subset of the
  Cantor space $2^\omega$. Let $X_s = X \times \{s\}$ for each
  $s \in 2^{<\omega}$, and $U_{\alpha,s} = U_\alpha \times \{s\}$.

  Finally, let \[\mathbb{X} = C \cup \bigcup_{s\in 2^{<\omega}} X_s\] be a
  tree of $2^{<\omega}$ copies of $X$, and where
  \[c_\alpha \cup \bigcup_{n < \omega} U_{\alpha, x_\alpha \restriction n}\]
  is an open set about each $c_\alpha$.
\end{ex}

\begin{prop}
$K \win \lfkpgame{\mathbb{X}}$.
\end{prop}

\begin{thm}(cor of G, game-theoretic proof by me)
$K\not\tactwin\lfkpgame{\mathbb{X}}$.
\end{thm}

\begin{thm}
$K\not\ktactwin{k}\lfkpgame{\mathbb{X}}$.
\end{thm}

>>>>

placeholder

% Results pertaining to the Locally Finite games related to $W$ games.

% \section{Characterizations using $\lfkpgame{X}$, $\lfklgame{X}$}

% \begin{thm}(G)
%   The following are equivalent for a locally compact space $X$:
%     \begin{itemize}
%       \item $X$ is paracompact
%       \item $\pl K \uparrow \lfklgame{X}$.
%     \end{itemize}
% \end{thm}

% \begin{thm}(G)
%   The following are equivalent for a locally compact space $X$:
%     \begin{itemize}
%       \item $X$ is metacompact
%       \item $\pl K \tactwin \lfkpgame{X}$.
%     \end{itemize}
% \end{thm}

% \begin{thm}(G)
%   The following are equivalent for a locally compact space $X$:
%     \begin{itemize}
%       \item $X$ is $\sigma$-metacompact
%       \item $\pl K \markwin \lfkpgame{X}$.
%     \end{itemize}
% \end{thm}

% \begin{obs}
%   The following are equivalent for any space $X$:
%     \begin{itemize}
%       \item $X$ is compact
%       \item $\pl K \ktactwin{0} \lfkpgame{X}$.
%     \end{itemize}
% \end{obs}

% \begin{thm}
%   $P \markwin G_{K,P}(X)$ where $X$ is a first-countable non-locally
%   countably compact space.
% \end{thm}

% \begin{thm}
%   $P \not\tactwin G_{K,P}(M)$ where $M$ is the metric fan space.
% \end{thm}

% \begin{thm}
%   The following are equivalent for any locally compact space $X$:
%     \begin{itemize}
%       \item $X$ is Lindel\"of.
%       \item $X$ is $\sigma$-compact.
%       \item $X$ is hemicompact.
%       \item $\pl K \prewin G_{K,L}(X)$.
%       \item $\pl K \prewin G_{K,P}(X)$.
%     \end{itemize}
% \end{thm}

% \begin{thm}
%   The following are equivalent for any Hausdorff $k$-space $X$:
%     \begin{itemize}
%       \item $X$ is hemicompact.
%       \item $X$ is $k_{\omega}$.
%       \item $\pl K \prewin \lfklgame{X}$.
%       \item $\pl K \prewin \lfkpgame{X}$.
%     \end{itemize}
% \end{thm}

% \section{Non-locally compact spaces}

% \begin{prop}
%   If $X=\omega\cup\mathcal{F}\subset\beta\omega$ (a non-$k$ space),
%   then $K\not\prewin \lfklgame{X}$.
% \end{prop}

% \begin{prop}
%   If a selective ultrafilter $\mathcal{F}$ exists (independent of ZFC),
%   then $K \not\prewin \lfkpgame{X}$
%   for $X=\omega \cup \{\mathcal{F}\}\subset \beta\omega$.
% \end{prop}

% \begin{thm}
%   Then there is an ultrafilter $\mathcal{F}$ such that
%   then $K \prewin \lfkpgame{X}$ and $K \tactwin \lfkpgame{X}$
%   for $X=\omega \cup \{\mathcal{F}\}\subset \beta\omega$.
% \end{thm}

% \begin{thm}
%   Let $M$ be the \term{metric fan}, a non-locally compact $k$ space.
%   Then $P \win \lfkpgame{M}$.
% \end{thm}

% \begin{thm}
%   Let $S$ be the \term{sequential fan}, a non-locally compact $k$ space.
%   Then $K \prewin \lfkpgame{S}$ and $K\tactwin \lfkpgame{S}$.
% \end{thm}

% (TODO: Maybe consider claim
% $K \prewin \lfkpgame{X}$ $\Rightarrow$ $X$ is a $k$-space)

% \section{Cantor tree space example}

% \begin{ex}
%   Let $X$ be a zero-dimensional, compact L-space
%   (hereditarally Lindeloff and non-separable).
%   It is a fact that there exists a point-countable collection
%   $\mathcal{U}=\{U_\alpha : \alpha<\omega_1\}$ of clopen sets in $X$, and it is
%   also true that any point-finite subcollection of $\mathcal{U}$ is countable.

%   Let $C = \{c_\alpha : \alpha <\omega_1\}$ be any uncountable subset of the
%   Cantor space $2^\omega$. Let $X_s = X \times \{s\}$ for each
%   $s \in 2^{<\omega}$, and $U_{\alpha,s} = U_\alpha \times \{s\}$.

%   Finally, let \[\mathbb{X} = C \cup \bigcup_{s\in 2^{<\omega}} X_s\] be a
%   tree of $2^{<\omega}$ copies of $X$, and where
%   \[c_\alpha \cup \bigcup_{n < \omega} U_{\alpha, x_\alpha \restriction n}\]
%   is an open set about each $c_\alpha$.
% \end{ex}

% \begin{prop}
% $K \win \lfkpgame{\mathbb{X}}$.
% \end{prop}

% \begin{thm}(cor of G, game-theoretic proof by me)
% $K\not\tactwin\lfkpgame{\mathbb{X}}$.
% \end{thm}

% \begin{thm}
% $K\not\ktactwin{k}\lfkpgame{\mathbb{X}}$.
% \end{thm}
